TCP Rax: Deep Reinforcement Learning for TCP Congestion Control

### 2018-01-29 tex/paper.tex
Add new config file

\begin{figure}
\begin{minipage}{\columnwidth}
\includegraphics[width=\columnwidth]{{{/home/max/repos/ns-allinone-2.35/ns-2.35/tcl/ex/congctrl/regular-tcp/nam_traces/figures/all_together_1_0}}}
\includegraphics[width=\columnwidth]{{{/home/max/repos/ns-allinone-2.35/ns-2.35/tcl/ex/congctrl/regular-tcp/nam_traces/figures/all_together_2_0}}}
\caption{One and two senders (from top to bottom) on a link with a stochastic loss rate of 1\%, a bandwidth/packet loss tradeoff of 2 on a link with 20\,Mbit/s bottleneck speed and 50\,ms RTT and a $\frac{1}{10}$ bandwidth delay buffer. Median in black and $\frac{1}{4}$ and $\frac{3}{4}$ quantile band in gray. It looks as if there is no stochastic loss in the very beginning of the flows, however, this is an artifact of the binning procedure: As the window is very small in the beginning, there are more flows in which no packet loss occurs whatsoever and thus the median is distorted.}
\label{fig:regular_tcps}
\end{minipage}
\end{figure}

>>>>

\begin{figure}
\begin{minipage}{\columnwidth}
\includegraphics[width=\columnwidth]{{{/home/max/repos/ns-allinone-2.35/ns-2.35/tcl/ex/congctrl/regular-tcp/nam_traces/figures/all_together_1_0}}}
\includegraphics[width=\columnwidth]{{{/home/max/repos/ns-allinone-2.35/ns-2.35/tcl/ex/congctrl/regular-tcp/nam_traces/figures/all_together_2_0}}}
\caption{Total throughput and loss rate ($\frac{\text{all packets lost}}{\text{all packets sent}}$) for one and two senders (from top to bottom) on a link with 20\,Mbit/s bottleneck speed and 50\,ms RTT and a $\frac{1}{10}$ bandwidth delay buffer. For a flow of 600\,s the maximum possible throughput is 12\,000\,Mbit}
\label{fig:regular_tcps}
\end{minipage}
\end{figure}
